Semantic Linearity in a Lazy Optimising Compiler

### 2024-02-12 icfp.tex
typos

\paragraph{$\Delta$-bound variables} Our development relies on the following characterization of $\D$-bound
variables:
A well-typed program with a linear variable ($\xl$) is equivalently
well-typed if the linear variable were instead $\D$-bound ($\xD$) with
usage environment $\D$, with $\D$ available in the linear context (and the unrestricted context updated accordingly).

>>>>

\paragraph{$\Delta$-bound variables} % Our development relies on a characterization of $\D$-bound
% variables
A well-typed program with a linear variable ($\xl$) is equivalently
well-typed if the linear variable were instead $\D$-bound ($\xD$) with
usage environment $\D$, with $\D$ available in the linear context (and the unrestricted context updated accordingly).
